---
title: "Business Analytics for Beginners Using R - Part I"
author: "Chinedu Okechukwu"
date: "10/26/2020"
output:
  pdf_document: default
  PDF_document: default
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Problem Statement

Investors need to move beyond the value-proposition of start-up companies in determining their success or failure to inform their investing strategies. As more information and data on start-ups is now available, investors want to discover factors from this information that affect the success of these start-up companies.

The primary objective of this data analytics project is to identify these factors or attributes of successful start-up companies by performing some analytical procedures on many informational attributes acquired on 472 start-up companies. The aim is to get the data into a more useable format to perform some form of exploration and statistical tests.
```{r prepocessing, include=FALSE}
library(dplyr)
library(Amelia)
startup<- read.csv(file="data/CAX_Startup_Data.csv", header=TRUE,as.is=T)

dim(startup)
startup[startup=="No Info"]<- NA
startup[startup=="Not Applicable"]<-NA
startup[startup==""]<- NA

NA_plot <- missmap(startup, legend = T, col = c('yellow','black'))
save(NA_plot,file = "fig/missing_value_plt.fig")
```

## Section 1: How the data was treated including missing value?

The csv file read to R contained 472 observation of 116 variables on start-up companies. Majority of the variables were classified as characters with a few as integers. 

Data frame had 264 rows of incomplete cases, i.e rows with NA values. Data also had values with “No Info” or blanks that needs to be changed to NA values. These values where replaced with NAs which increased the number of rows with incomplete cases to 456.The missing value plot is shown in Figure below.
```{r pressure, echo=FALSE}
missmap(startup, legend = T, col = c('yellow','black'))
```
__Fig 1 Missing Value Plot__


I handled the 15% missing value as follows:  

1. I removed variables that had more than 40% missing values which resulted in the removal of the following 3 variables I calculated the proportion of missing values for each variable and set a rule to keep variables that have 40% or less missing values. The following columns(variables were removed as a result)

```{r removal of variables with >40% NAs, include=FALSE}
nrow(startup[!complete.cases(startup),])

# converting column as date.....
startup$Est..Founding.Date <- as.Date(startup$Est..Founding.Date, "%m/%d/%Y")
startup$Last.Funding.Date <- as.Date(startup$Last.Funding.Date, "%m/%d/%Y")



# display column header of data
colnames(startup) 

# noting columns that needs to be converted to numeric
col<- c(3:5,10,11,18:23,25,61,66,72,74,88,92,94:96,98,99,102:116)

# using for loop to convert column as numeric
for(i in col)
{
  startup[,i]<-as.numeric(startup[,i])
}

# Percent missing value for each variable
mis_val<-sapply(startup, function(x) sum(is.na(x)))
percent_mis<-as.data.frame(round((mis_val/nrow(startup))*100,1))



name<-row.names(percent_mis)
pcnt_mis_var<-cbind(name,percent_mis)
row.names(pcnt_mis_var)<-NULL
colnames(pcnt_mis_var)<-c("variable","Percent.Missing")

var_dropped<-pcnt_mis_var%>%filter(percent_mis>40)

save(var_dropped, file = "fig/variables_40%_nas.fig")
# keeping only variables with less than 40% missing
removed_variable <- as.data.frame(pcnt_mis_var$variable[which(pcnt_mis_var$Percent.Missing<=40)])
new_var<-as.character(pcnt_mis_var$variable[which(pcnt_mis_var$Percent.Missing<=40)])
new_startup<-startup[new_var]


```

```{r echo=FALSE, fig.height=5, fig.width=10}
var_dropped
```

2.  I added back the 'Survival.through.recession..based.on.existence.of.the.company.through.recession.times' and renamed the variable as 'Survived.recessions'. The variable is key to recomputing the 'Age.of.company' to properly reflect the life of the company. 

3.  I imputed the remaining missing values with the median for numeric variables and the mode for categorical variables. The survived.recessions was imputed by referencing the Dependent variable, ideally most firms that failed with their founding date prior to the Dot.com bubble of 2000-2001 and great recession of 2008-2009 should have a value of 'No' and 'Yes' if the are successful.


```{r include=FALSE}
ncol(startup) # 116
ncol(new_startup)#113


# separate data frame for more than 40% missing
other_var<-as.character(pcnt_mis_var$variable[which(pcnt_mis_var$Percent.Missing>40)])
other_data<-startup[other_var]

new_startup$survived.recessions <- other_data$Survival.through.recession..based.on.existence.of.the.company.through.recession.times

#Impute missing values for Survived.recessions based on year founding, and Dependent.Company.Status
new_startup%>%select(Dependent.Company.Status,survived.recessions,Age.of.company.in.years,year.of.founding,Gartner.hype.cycle.stage)%>%
  filter(Dependent.Company.Status=='Failed'& year.of.founding<2008)

for (i in 1:length(new_startup$survived.recessions))
{
  if(is.na(new_startup$survived.recessions[i]) & is.na(new_startup$year.of.founding[i])){
    is.na(new_startup$survived.recessions[i])}
  else if(is.na(new_startup$survived.recessions[i]) & new_startup$year.of.founding[i] <= 2008 &
             new_startup$Dependent.Company.Status[i]=='Failed') {
    new_startup$survived.recessions[i]<- 'No'}
  else if(is.na(new_startup$survived.recessions[i]) & new_startup$year.of.founding[i] >2008){
    new_startup$survived.recessions[i]<- 'Post-Recession'}
  else {new_startup$survived.recessions[i]}
  } 


#Recalculating age of company

for (i in 1:length(new_startup$Age.of.company.in.years))
{
  if(is.na(new_startup$Age.of.company.in.years[i]) & is.na(new_startup$year.of.founding[i])){
    new_startup$Age.of.company.in.years[i]}
  else if(new_startup$year.of.founding[i] < 2001 & new_startup$survived.recessions[i]== 'No' &
          !is.na(new_startup$Time.to.1st.investment..in.months.[i])) {
    new_startup$Age.of.company.in.years[i]<- ceiling((new_startup$Time.to.1st.investment..in.months.[i])/12)}
  else if(new_startup$year.of.founding[i] >= 2001 & new_startup$survived.recessions[i]== 'No' &
          !is.na(new_startup$Time.to.1st.investment..in.months.[i])) {
    new_startup$Age.of.company.in.years[i]<- ceiling((new_startup$Time.to.1st.investment..in.months.[i])/12)}
  else {new_startup$Age.of.company.in.years[i]}
} 

#

# writing new data as csv file
save(new_startup,file = "rda/startup2_NA.rda")
```


##  Section 2: Details of additional features created

I created two additional variables- Investor.count from as a sum of the total number investors for each startup and “Industry. Count” as the total number of industries a startup belongs to.I then dropped their originating variables along with the following:  
. Company_Name  
.	Short.Description.of.company.profile  
.	Est..Founding.Date & Last.Funding.Date (Age of company is already in the data)  
.	Specialization.of.highest.education- (multiple values but highest education will suffice)  
.	Time.to.maturity.of.technology..in.years (this had only one value, hence low variability)  

The categorical variables were encoded as factors.
```{r preprocessing numeric variables, include=FALSE}
library(dplyr)
library(tidyverse)

# Separate data frame for numeric variables, use the select_if()
new_startup <-read.csv('na_processed_data.csv')
cnt_df <- select_if(new_startup,is.numeric)
str(cnt_df)

# # separate data frame for character variables
# cnt_var<-colnames(cnt_df)
# var <- colnames(new_startup) %in% cnt_var 
# char_df <- new_startup[!var]
# 
# str(char_df)

# checking distribution of continuous variable for outlier detection and missing values
summary(cnt_df)

head(cnt_df)
glimpse(cnt_df)




```


```{r preprocessing categorical variables, include=FALSE}
library(dplyr)
library(tidyverse)

# Separate data frame for numeric variables, use the select_if()
new_startup <-read.csv('na_processed_data.csv')
cnt_df <- select_if(new_startup,is.numeric)


# separate data frame for character variables
cnt_var<-colnames(cnt_df)
var <- colnames(new_startup) %in% cnt_var 
char_df <- new_startup[!var]

# checking distribution of categorical variable for missing values
table(char_df$Local.or.global.player,useNA="always")
table(char_df$Gartner.hype.cycle.stage, useNA = "always")

# convert a variable to uppercase
char_df$Local.or.global.player<-toupper(char_df$Local.or.global.player)

cols <- c(2:3,6:72)
for(i in cols)
{
  char_df[,i]<-toupper(char_df[,i])
}

# trimming white-spaces
char_df$Local.or.global.player<-trimws(char_df$Local.or.global.player)

# converting character variables to factors
char_df$Local.or.global.player<- as.factor(char_df$Local.or.global.player)
char_df$Degree.from.a.Tier.1.or.Tier.2.university.<-as.factor(char_df$Degree.from.a.Tier.1.or.Tier.2.university.)
char_df$Number.of..of.Partners.of.company<-as.factor(char_df$Number.of..of.Partners.of.company)
char_df$Cloud.or.platform.based.serive.product.<-as.factor(char_df$Cloud.or.platform.based.serive.product.)
char_df$Average.size.of.companies.worked.for.in.the.past <- as.factor(char_df$Average.size.of.companies.worked.for.in.the.past)

colnames(char_df)
# using for loop to convert common variable vlaues as factors
yes_no <- c(7,12,14,16:19,21,23,25,29,31:40,45,49:50,60:61,63:70,72)
for(i in yes_no)
{
  char_df[,i]<-as.factor(char_df[,i])
}
hi_lo <- c(13,43,44,46,52,56:59,62)
for(i in hi_lo)
{
  char_df[,i]<-as.factor(char_df[,i])
}

other_factors <- c(10,11,20,22,24,28,41,42,47)
for(i in other_factors)
{
  char_df[,i]<-as.factor(char_df[,i])
}


# Create additional features like counting number of investors for company
char_df$Investor.count<-length(strsplit(char_df$Investors, "|",fixed=T))
for (i in (1:length(char_df$Investors)))
{
  if(is.na(char_df$Investors[i])==T){
    char_df$Investor.count[i]<- NA}
  else{
    lst<-strsplit(char_df$Investors[i], "|", fixed=T)
    char_df$Investor.count[i]<-length(lst[[1]])
  } }

# Create additional features like counting number of industries a startup belongs to
char_df$Industry.count<-length(strsplit(char_df$Industry.of.company, "|",fixed=T))
for (i in (1:length(char_df$Industry.of.company)))
{
  if(is.na(char_df$Industry.of.company[i])==T){
    char_df$Industry.count[i]<- NA}
  else{
    lst<-strsplit(char_df$Industry.of.company[i], "|", fixed=T)
    char_df$Industry.count[i]<-length(lst[[1]])
  } }

char_df$Investor.count<- as.factor(char_df$Investor.count)
char_df$Dependent.Company.Status <- as.factor(char_df$Dependent.Company.Status)
char_df$Focus.functions.of.company <- as.factor(char_df$Focus.functions.of.company)
char_df$Industry.count <-as.factor(char_df$Industry.count)
char_df$Disruptiveness.of.technology <-factor(char_df$Disruptiveness.of.technology, levels = (c("LOW","MEDIUM","HIGH")) )


# function to calculate mode
Mode <- function(x) {
  u <- unique(na.omit(x))  # took me a while had to include this as I had NAs as highest frequency
  u[which.max(tabulate(match(x, u)))]
}

# Filling missing values with mode
char_df$Local.or.global.player[is.na(char_df$Local.or.global.player)]<-Mode(char_df$Local.or.global.player)
table(char_df$Local.or.global.player)
char_df$Gartner.hype.cycle.stage[is.na(char_df$Gartner.hype.cycle.stage)] <- Mode(char_df$Gartner.hype.cycle.stage)
table(char_df$Gartner.hype.cycle.stage)


#applying mode of each variable to their missing values

for(char in 1:ncol(char_df)) {
  char_df[is.na(char_df[,char]),char] <-Mode(char_df[,char])
}

save(char_df,file = "rda/char_df_processed.rda")
# add back target variable to continuous data 
cnt_df$Dependent.Company.Status <- new_startup$Dependent.Company.Status

save(cnt_df,file="rda/cnt_var_processed.rda")

```


##  Section 3: Graphical presentation of your exploration and its interpretation

I used the histogram and boxplots to visualize the distribution of the continuous variables and also to check for outliers using facet-wraps in batches of 4-6 variables. I renamed some of the variables that were long.

```{r include=FALSE}

cnt_df<-cnt_df%>%rename(Investors.Angel.or.VC= Number.of.Investors.in.Angel.and.or.VC,
                        Repeat.Investors =Number.of.of.repeat.investors,
                        No.of.Advisors = Number.of.of.advisors,
                        No.of.Cofounders= Number.of.Co.founders,
                        Investors.in.Seed =Number.of.Investors.in.Seed)
cnt_df$Investor.count <- as.numeric(char_df$Investor.count)

                       


```


```{r echo=FALSE, fig.height=5, fig.width=10, message=FALSE, warning=FALSE}

cnt_df%>%
  select(c(6,7,9,12,42,42))%>%
  gather(-Dependent.Company.Status,key = key,value = value)%>%
  ggplot(aes(value,fill=Dependent.Company.Status))+
  ylab("Frequency") +
  facet_wrap(~key,scales = 'free') +
  geom_histogram(alpha=0.2,color ='black')+
  scale_x_continuous(trans = "sqrt" ) +
  geom_vline(aes(xintercept= median(value, na.rm=T)),   
             color="red", linetype="dashed") +
  theme_bw()

cnt_df%>%
  select(c(6,7,9,12,42,43))%>%
  gather(-Dependent.Company.Status, key = "var",value = "value")%>%
  ggplot(aes(x = value,y = Dependent.Company.Status, 
             fill=Dependent.Company.Status))+
  geom_boxplot()+
  facet_wrap(~var,scales = 'free') +
  scale_x_continuous(trans = "sqrt" ) +
  theme_bw()

```
_Figure 1 Investor variable set_

The histograms are skewed to the right and there boxplots showed outliers that needs to be capped. This was achieved using the maximum values of each variable with respect to their categories.The plots also revealed that on average Successful startups attracted more investors in total and in all categories than failed startups, except fot the investor.count variable were it looks as if there is little or no difference in means. This variable we will investigate further for statistical significance in selecting our predictor variable.


```{r echo=FALSE, fig.height=5, fig.width=10, message=FALSE, warning=FALSE, paged.print=TRUE}

cnt_df%>%
  select(c(4,11,23,42))%>%
  gather(-Dependent.Company.Status,key = key,value = value)%>%
  ggplot(aes(value,fill=Dependent.Company.Status))+
  ylab("Frequency") +
  facet_wrap(~key,scales = 'free') +
  geom_histogram(alpha =0.5,color ='black',binwidth = 1)+
  geom_vline(aes(xintercept=median(value, na.rm=T)),   
             color="red", linetype="dashed") +
  scale_x_continuous(trans = "sqrt" )+
  theme_bw()

cnt_df%>%
  select(c(4,11,23,42))%>%
  gather(-Dependent.Company.Status, key = "var",value = "value")%>%
  ggplot(aes(x = value,y = Dependent.Company.Status, 
             fill=Dependent.Company.Status))+
  geom_boxplot()+
  facet_wrap(~var,scales = 'free') +
  scale_x_continuous(trans = "sqrt" )+
  theme_bw()
```
_Figure 2 Employee variable set_

For the employee variable set, the plots reveal a right tail while the boxplots suggest little or no difference in means between the two classes of dependent variable. This will also be investigated for their statistical significance towards variable selection.  


```{r echo=FALSE, fig.height=5, fig.width=10, paged.print=FALSE}

cnt_df<-cnt_df%>%rename(Last.Round.Funding.Amt = Last.Funding.Amount,
                        Avg.time.to.inv.all.rounds =Avg.time.to.investment...average.across.all.rounds..measured.from.previous.investment)%>%
  mutate( Last.Round.Funding.Amt=Last.round.of.funding.received..in.milionUSD.*1000000)

```


```{r echo=FALSE, fig.height=5, fig.width=10, message=FALSE, warning=FALSE, paged.print=TRUE}
cnt_df%>%
  select(c(2,5,25,26,42))%>%
  gather(-Dependent.Company.Status,key = key,value = value)%>%
  ggplot(aes(value,fill=Dependent.Company.Status))+
  ylab("Frequency") +
  facet_wrap(~key,scales = 'free') +
  geom_histogram(alpha =0.5,color ='black')+
  geom_vline(aes(xintercept=median(value, na.rm=T)),   
             color="red", linetype="dashed") +
  scale_x_continuous(trans = "sqrt" )+
  theme_bw()

cnt_df%>%
  select(c(2,5,25,26,42))%>%
  gather(-Dependent.Company.Status, key = "var",value = "value")%>%
  ggplot(aes(x = value,y = Dependent.Company.Status, 
             fill=Dependent.Company.Status))+
  geom_boxplot()+
  facet_wrap(~var,scales = 'free') +
  scale_x_continuous(trans = "sqrt" )+
  theme_bw()


```
_Fig 3 Age of Company, Time to invest and Last Round Funding Amount_


```{r echo=FALSE, fig.height=5, fig.width=10, message=FALSE, warning=FALSE}
cnt_df%>%
  select(c(27:32,42))%>%
  gather(-Dependent.Company.Status,key = key,value = value)%>%
  ggplot(aes(value,fill=Dependent.Company.Status))+
  ylab("Frequency") +
  facet_wrap(~key,scales = 'free') +
  geom_histogram(alpha =0.5,color ='black')+
  geom_vline(aes(xintercept=median(value, na.rm=T)),   
             color="red", linetype="dashed") +
  scale_x_continuous(trans = "sqrt" )+
  theme_bw()

cnt_df%>%
  select(c(27:32,42))%>%
  gather(-Dependent.Company.Status, key = "var",value = "value")%>%
  ggplot(aes(x = value,y = Dependent.Company.Status, 
             fill=Dependent.Company.Status))+
  geom_boxplot()+
  facet_wrap(~var,scales = 'free') +
  scale_x_continuous(trans = "sqrt" )+
  theme_bw()

```

```{r echo=FALSE, fig.height=5, fig.width=10, message=FALSE, warning=FALSE}
cnt_df%>%
  select(c(33:39,19,42))%>%
  gather(-Dependent.Company.Status,key = key,value = value)%>%
  ggplot(aes(value,fill=Dependent.Company.Status))+
  ylab("Frequency") +
  facet_wrap(~key,scales = 'free') +
  geom_histogram(alpha =0.5,color ='black')+
  geom_vline(aes(xintercept=median(value, na.rm=T)),   
             color="red", linetype="dashed") +
  scale_x_continuous(trans = "sqrt" )+
  theme_bw()

cnt_df%>%
  select(c(33:39,19,42))%>%
  gather(-Dependent.Company.Status, key = "var",value = "value")%>%
  ggplot(aes(x = value,y = Dependent.Company.Status, 
             fill=Dependent.Company.Status))+
  geom_boxplot()+
  facet_wrap(~var,scales = 'free') +
  scale_x_continuous(trans = "sqrt" )+
  theme_bw()

```

_Fig 5 skills set variables_  

The plots for the percent skills for 'Consulting,Finance and Law revealed that close to 90% of startups have no skill in this area and hence may not be a great predictor of the target variable. These variables will be dropped. 
The boxplots of percent skills for entrepreneurship,operations,Domain, Marketing and Sales suggests there may be little or no difference in the means for the two classes.This will be investigated further using the t-test. 

```{r include=FALSE}
summary(cnt_df$Team.size.all.employees)
quantile(cnt_df$Team.size.all.employees, probs = seq(0, 1, by= 0.05),na.rm=T)

# further exploration to determine cutoff for capping
quantile(cnt_df$Team.size.all.employees, probs = seq(.9, 1, by= 0.01),na.rm=T)

quants <- seq(0,1,.1)

#using apply function to get the quantiles of the variables in a dataframe
qunt_df <- t(apply( cnt_df[2:36] , 2 , quantile , probs = quants , na.rm = TRUE ))
qunt_df <- as.data.frame(qunt_df[c(3:4,11,15,16,20,22:24),])

quantile(cnt_df$Percent_skill_Engineering, probs = seq(0.9, 1, by= 0.01),na.rm=T)


# capping some outlier values  
cnt_df$Team.size.all.employees[cnt_df$Team.size.all.employees>106.4]<-106
cnt_df$Internet.Activity.Score[cnt_df$Internet.Activity.Score<0]<-0
cnt_df$Internet.Activity.Score[cnt_df$Internet.Activity.Score>100]<-100
cnt_df$Employee.Count[cnt_df$Employee.Count>211.8] <-211
cnt_df$Skills.score[cnt_df$Skills.score>53.45]<-53
cnt_df$Number.of.Recognitions.for.Founders.and.Co.founders[cnt_df$Number.of.Recognitions.for.Founders.and.Co.founders>
                                                             107.5]<-107
cnt_df$Employees.per.year.of.company.existence[
  cnt_df$Employees.per.year.of.company.existence>76.14
]<- 76
cnt_df$Time.to.1st.investment..in.months.[cnt_df$Time.to.1st.investment..in.months.>48]<-48
cnt_df$Avg.time.to.inv.all.rounds[ cnt_df$Avg.time.to.inv.all.rounds>48] <- 48

cnt_df$Percent_skill_Entrepreneurship[cnt_df$Percent_skill_Entrepreneurship>30.4]<-30
cnt_df$Percent_skill_Engineering[cnt_df$Percent_skill_Engineering>76]<-75

# Missing value treatemnt using median
cnt_df$Team.size.all.employees[is.na(cnt_df$Team.size.all.employees)]<-median(cnt_df$Team.size.all.employees,na.rm=T)
any(is.na(cnt_df$Team.size.all.employees))

# Using median for NA values
impute.med <- function(x) {
  z <- median(x, na.rm = TRUE)
  x[is.na(x)] <- z
  return(x)
}

# Applying median value to missing values in dataframe
nums <-c(1:36)
cnt_df[nums] <- sapply(cnt_df[nums], function(x){
  if(any(is.na(x))){
    impute.med(x)
  } else {
    x
  }
}
)

```



```{r echo=FALSE, message=FALSE, warning=FALSE}


```



##  Section 4: Summary of your exploration 

In this project, we prepared the raw data for further analysis by looking at the structure of the data to better understand the variables, the state of the values and how complete they are. We removed a few variables and some observations that had a greater percentage of missing values, classified the numeric variables and performed some summary statistics to check for outliers in numeric variables which were replaced with the reasonable values, and missing values (NAs) substituted with the median. The missing values in the categorical variables were also substituted with the mode. 

Hypothesis testing were conducted to observe the mean of the two groups of startups to ensure that they are different. Two-sided t-tests were conducted on the continuous variables and 19 out of 42 variables had p-values below 0.05% and were selected for use. See table below.

```{r echo=FALSE}

library(broom)
ab <-t.test(Team.size.all.employees~Dependent.Company.Status, data=cnt_df)

#select variables that have the two samples means almost equal for t-test and variabled seletion
# efficiently selecting relevant variables from t-test results

var_seleection <- cnt_df%>%
  gather(-Dependent.Company.Status, key = "var",value = "value")%>%
  group_by(var)%>%
  do(tidy(t.test(value~ Dependent.Company.Status, data=.)))

var_selection <-as.data.frame(var_seleection)
var_less_0.05<- var_seleection%>%filter(p.value <= 0.05)%>%select(statistic,p.value)
var_above_0.05<- var_seleection%>%filter(p.value >0.05)

var_less_0.05
### Select Variables with p-value below 0.05
new_cnt_var<-var_less_0.05$var

cnt_df_new<-cnt_df[,new_cnt_var]



```
_Table 4.1 Continuous Variables selected with P Value less than 0.05_




I also executed a chi-squared test was on the categorical variables to select 51 variables for the model. see Table below.


```{r echo=FALSE}
# tabulating data for chi-sq test
tab<- table(char_df$Dependent.Company.Status,char_df$Local.or.global.player)

# chi-sq test
tidy(chisq.test(tab))

# apply simultaneously to select variables

chisq<-as.data.frame(lapply(char_df[,-1], function(x) chisq.test(table(x,char_df$Dependent.Company.Status), 
                                                                 simulate.p.value = TRUE)$p.value))

row.names(chisq)<- "p.values"
chisq_t <-as.data.frame(t(chisq))
pv.less.0.05 <- t(chisq_t%>%filter(p.values <0.05))
t.pv.less.0.05 <-as.data.frame(t(pv.less.0.05))
head(t.pv.less.0.05,10)
char.cols.sel <- colnames(pv.less.0.05)


new.char_df <-char_df[,c(char.cols.sel,"Dependent.Company.Status")]

# combine the new continuous variables dataframe with the categorical variables dataframe

final_df <-cbind(cnt_df_new,new.char_df)

write.csv(final_df,"startup_final_data.csv",row.names=F)
```

The continuous variables data frame with the selected variables were combined with the categorical variables data frame to make-up a data frame of 75 variables (including the outcome variable and 472 observations to develop the machine learning model. 
